---
title: "Group Project: Agriculture in Turkey - EDA"
date: "19 November 2022"
format:
  html:
    toc: true
    toc-depth: 3
    toc-float: true
    number-sections: false
---

```{=html}
<style>
    body { 
    font-family: Calibri;
    text-align: justify;
    font-size: 11pt;
    div.hidecode + pre {display: none}
    }
</style>
```
::: hidecode
```{r setup, output=FALSE,echo=FALSE,warning = FALSE}
knitr::opts_chunk$set(warning = FALSE)
Sys.setlocale(locale = "en_US.UTF-8")
options(dplyr.summarise.inform = FALSE)
```
:::

Agriculture in Turkey - EDA is the part 2 of the Group Project: Agriculture in Turkey

We start by  loading our dataset that we prepare in the **Group Project: Agriculture in Turkey - Preprocessing**

## Load the Data
```{r}
# Prepare data
tarim <- readRDS("data//tarim.rds")
meyve <- readRDS("data//meyve.rds")
sebze <- readRDS("data//sebze.rds")
tahil <- readRDS("data//tahil.rds")
```
## Questions 
In this work, we seek to answer these questions;

1- Are the areas we use for agriculture decreasing?
2- What is the regional distribution of increases and decreases?
3- Is our production amount decreasing?
4- Is our production efficiency increasing?
5- What will our agricultural production be in the future?